How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-12 tse-paper/content.tex
Fix build

\noindent
\textbf{Our work contributes:}
\begin{itemize}
  \item A tool unifying several chunk retrieval techniques namely:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS).
        \end{itemize}
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique.
\end{itemize}

@@

\todo{structure overview of article}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
	\caption{The different entities related to a CI build. \todo{mention in text or remove}}
	\label{fig:build-overview}
\end{figure}

@@

\begin{figure}[!t]
		\centering
		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}

>>>>

\noindent
\textbf{Our work contributes:}
\begin{itemize}
  \item A tool with three prototypical implementations of chunk retrieval techniques:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS).
        \end{itemize}
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique.
\end{itemize}

@@

%\todo{structure overview of article}

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=\columnwidth, clip]{img/build-overview.pdf}
	\caption{The different entities related to a CI build.
        %\todo{mention in text or remove}
        }
	\label{fig:build-overview}
\end{figure}

@@

\begin{figure}[!t]
		\centering
		\includegraphics[width=0.75\columnwidth, clip]{img/big-study/failure-reason-pbe.pdf}
		\caption{Results of chunk retrieval with PBE.}
		\label{fig:failure-reason-PBE}
\end{figure}
